### 2017-07-03 sheets/talk-10/sheet-10.tex
More extensions.

>>>>

\begin{exercise}
  Let $\cat A$ be a locally small CCC. Use the Yoneda embedding to show that for any objects $A,B,C\in\cat A$,
  \begin{align*}
    (A\times B)^C\iso A^C\times B^C
  \end{align*}
  If $\cat A$ also has binary coproducts, show that also
  \begin{align*}
    A^{B+C}&\iso A^B\times A^C\\
    (A\times B)+(A\times C)&\iso A\times (B+C)
  \end{align*}
\end{exercise}

\begin{exercise}
  Let $\cat B$ be a category and $J\from\cat C\to D$ a functor. There is an induced functor
  \begin{align*}
    J\of -\from[\cat B,\cat C]\to [\cat B,\cat D]
  \end{align*}
  defined by composition with $J$.
  \begin{enumerate}
  \item Show that if $J$ is full and faithful then so is $J\of -$.
  \item Deduce that if $J$ is full and faithful and $G,G'\from\cat B\to\cat C$ with $J\of G\iso J\of G'$ then $G\iso G'$.
  \item Now deduce that right adjoints are unique: if $F\from \cat A\to\cat B$ and $G,G'\from\cat B\to \cat A$ with $F\dashv G$ and $F\dashv G'$ then $G\iso G'$. 
    \hint{The Yoneda embedding is full and faithful.}
  \end{enumerate}
\end{exercise}

\begin{definition}{Preservation of Limits}
  Let $\mathbf I$ be a small category. A functor $F\from \cat A\to\cat B$ \emph{preserves colimits of shape $\mathbf I$} if for all diagrams $D\from\mathbf I\to\cat A$ and all cocones $(D(I)\xrightarrow{p_I}A)_{I\in \mathbf I}$ on $D$,
  \begin{align*}
    &(D(I)\xrightarrow{p_I}A)_{I\in \mathbf I} \text{ is a limit cone on $D$ in } \cat A\\
    \Longrightarrow&(F\of D(I)\xrightarrow{F(p_I)}F(A))_{I\in \mathbf I} \text{ is a limit cone on $F\of D$ in } \cat A
  \end{align*}

  A functor $F\from \cat A\to\cat B$ \emph{preserves limits} if it preserves limits of shape $\mathbf I$ for all small categories $\mathbf I$.
\end{definition}
\begin{exercise}
  Fill in some of the missing details in the proof that for any small category $\cat A$ the presheaf category $[A^\op,\Set]$ is cartesian closed:
  \begin{enumerate}
  \item Show that for any $A\in\cat A$, $H_A$ preserves colimits. As a consequence $$H_A(\lim_{\to\mathbf I} D)\iso \lim_{\to\mathbf I}(H_A\of D)$$ for all shapes and diagrams.
    \hint{It suffices to show that it preserves all products and equalizers.}
  \item Let $F\from \cat A\to\Set$ be a presheaf. Show that the functor $-\times F\from [\cat A^\op,\Set]\to[\cat A^\op,\Set]$ preserves colomits. That is: For any small category $\mathbf I$ and functor $D\from\mathbf I\to [\cat A^\op,\Set]$,
    \begin{align*}
      \lim_{\to \mathbf I} (D\times F)\iso (\lim_{\to \mathbf I} D)\times F.
    \end{align*}
    You may assume that $[\cat A^\op,\Set]$ has all limits. (In particular limits, which are functors $\cat A^\op\to\Set$, are taken ``pointwise'': $$\left(\lim_{\to I\in\mathbf I} D(I)\right)(A) \iso \lim_{\to I\in\mathbf I} \left(D(I)(A)\right)$$ for all shapes and diagrams.)
    \hint{TODO}
  \end{enumerate}
\end{exercise}

\begin{exercise}
  Let $\cat A$ be a small category. Prove that the representable functors \emph{generate} the presheaf category $[\cat A^\op,\Set]$ in the folowing sense: Given any objects $F,G\in[\cat A^\op,\Set]$ and natural transformations $\alpha,\beta\from F\to G$, if for every representable functor $H_A$ and natural transformation $\gamma\from H_A\to F$, one has $\alpha\of\gamma=\beta\of\gamma$, then $\alpha=\gamma$. Thus, the arrows in $[\cat A^\op,\Set]$ are determined by their effect on generalized elements based at representables.
\end{exercise}

\begin{exercise}
  special case of yoneda embedding: groups vs. Caley-representation
\end{exercise}
